---
title: '<div class="jumbotron"><h1 class="title toc-ignore display-3" align="center">Data Visualisation in R</h1><p class="lead" align="center">Danielle Navarro</p></div>'
output:
  html_document:
    theme: flatly
    highlight: textmate
    css: mystyle.css
pagetitle: "Data Visualisation"
---

```{r,echo=FALSE}
rm(list=objects()) # start with a clean workspace
```

This site has links to all the course materials associated with the workshop on *"Data visualisation in R, from ggplot2 to gganimate"* as part of the [2019 satRday in Johannesburg](https://joburg2019.satrdays.org) meeting. It's intended to be a hands on workshop will provide an introduction to data visualisation in R. The core of the workshop will focus on creating clean data visualisations with `ggplot2`, and turning them into animations with gganimate. The workshop is aimed at a beginner to intermediate level. Some prior familiarity with `tidyverse` would be helpful but not assumed.

## Package dependencies

Participants will need a recent installation of R and RStudio. The package dependencies are listed below, all of which should be available on CRAN. To verify that you have them installed you can run the following:

```{r, eval=FALSE}
library(tidyverse)
library(here)
library(hexbin)
library(gganimate)
library(sf)
library(usethis)
library(scico)
```

## Course materials

The course materials are can be downloaded as a zip file [here](./datavis.zip), or alternatively to download them directly within R and automatically open the correct project file:

```{r, eval=FALSE}
# install.packages(usethis) 
usethis::use_course("https://djnavarro.github.io/satrdayjoburg/datavis.zip")
```

The current version of the course is not *quite* complete (my slides are missing and one set of exercises isn't done yet) but it should cover most of the worskhop content.


